% !TEX root = ../thesis.tex

\pdfbookmark[0]{Abstract}{Abstract}
\chapter*{Abstract}
\vspace*{-10mm}

This thesis reviews unconventional applications of deep learning, focusing on the separation of style and content in images.
By using an already trained convolutional neural network, \citeauthor{Gatys2015B}'s Neural Style, a novel algorithm for style transfer, consistently disentangles style and content from two different images and combines them in artistic compositions of high perceptual quality.
With the intention to appreciate its achievements, we provide an introduction to basic theoretical concepts and common techniques in deep learning as well as the necessary background in object recognition and artistic rendering.
Also, we survey ongoing research triggered by the methods introduced by Neural Style.
To end with, and inspired by said methods, we propose future work in the direction of algorithmic aesthetics.


\vspace*{20mm}
{\usekomafont{chapter}Abstract (Spanish)} \\

Esta tesis estudia usos poco comunes del \emph{deep learning}, centrándose en la separación del estilo y el contenido en imágenes.
Utilizando una red neuronal convolucional ya entrenada, Neural Style, un innovador algoritmo propuesto por \citeauthor{Gatys2015B}, consigue desenredar de forma consistente el estilo y el contenido de dos imágenes y los combina en composiciones artísticas de alta calidad perceptual.
Con la intención de poder apreciar sus logros, damos una introducción a conceptos teóricos y técnicas comunes en \emph{deep learning} así como el trasfondo necesario en reconocimiento de objetos y renderizado artístico.
También examinamos otras investigaciones que han surgido a raíz de los métodos planteados por Neural Style.
Por último, e inspirados por dichos métodos, proponemos trabajo futuro en la dirección del campo de la estética algorítmica.
